### 2018-08-24 Sections/cryptowars.tex
Voting fig

@@

Alg.~\ref{alg:quantum_voting} describes a quantum implementation for anonymous surveys, using the protocol described by \cite{bib:VaccaroVoting}.

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function QuantumVoting($\ket{B_0}$):
\begin{enumerate}
\item For $N$ voters, the \textit{ballot state} is prepared,
\begin{align}
\ket{B_0} = \frac{1}{\sqrt{N+1}}\sum_{n=0}^N \ket{N-n}_T\ket{n}_V,	
\end{align}
in the photon-number basis, where $T$ is held by the tallyman and $V$ is held by the voters.
\item Each voter $j$ applies their vote operator,
\begin{align}
	\hat{v}_j = e^{i\pi\hat{n}_V \frac{\nu_j}{N+1}},
\end{align}
where $\hat{n}_V$ is the photon-number operator for mode $V$, and $\nu_j$ is the amount cast for the $j$th voters vote.
\item Following the $m$th vote the ballot state is,
\begin{align}
	\ket{B_m} = \frac{1}{\sqrt{N+1}}\sum_{n=0}^m e^{in\Delta_m} \ket{N-n}_T\ket{n}_V,
\end{align}
where,
\begin{align}
\Delta_m = \frac{2\pi}{N+1}\sum_{j=1}^m \nu_j,
\end{align}
is a scaled sum of the votes.
\item After the $m$th vote the state observed by the tallyman is,
\begin{align}
\mathrm{tr}_V(\ket{B_m}\bra{B_m}) = \frac{1}{N+1}\sum_{n=0}^N \ket{n}_T\bra{n}_T,	
\end{align}
which contains no voting information, and similarly for the voters' reduced state.
\item After all $N$ voters have voted, the voter state $V$ is transferred to the tallyman $T$.
\item Define the tally operator as,
\begin{align}
\hat{T} = \sum_{n=0}^N n\ket{T_n}\bra{T_n},	
\end{align}
where,
\begin{align}
\ket{T_n} = \frac{1}{\sqrt{N+1}}\sum_{j=0}^N e^{inj\frac{2\pi}{N+1}}\ket{N-j}\ket{j}.	
\end{align}
\item The tallyman finds the expectation value of the tally operator,
\begin{align}
\bra{B_N}\hat{T}\ket{B_N} = \sum_{j=1}^N \nu_j,
\end{align}
yielding the sum of all the votes.
\item $\Box$
\end{enumerate}
}
\end{mdframed}
\caption{Protocol for performing secure quantum anonymous surveying.} \label{alg:quantum_voting}\index{Quantum voting}
\end{table}

>>>>

The security of voting systems, and the anonymity of their voters are a pressing issue in the modern world, and there have been countless high-profile instances of voting systems being compromised nefariously.

@@

Fig.~\ref{fig:quantum_voting} and Alg.~\ref{alg:quantum_voting} describe a quantum implementation for anonymous surveys, using the protocol described by \cite{bib:VaccaroVoting}.

\begin{figure}[!htbp]
\includegraphics[width=0.35\textwidth]{quantum_voting}
\caption{Protocol for quantum voting via anonymous surveying. The tallyman prepares the entangled state $\ket{B_0}$, half of which is shared with the votes. The voters each perform local phase-shift operations on the voters' half of the state, as per Alg.~\ref{alg:quantum_voting}. The phase-transformed state is then returned to the tallyman, who is able to extract the phase and hence the cumulative vote.}\label{fig:quantum_voting}\index{Quantum voting}	
\end{figure}

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function QuantumVoting($\ket{B_0}$):
\begin{enumerate}
\item For $N$ voters, the \textit{ballot state} is prepared,
\begin{align}
\ket{B_0} = \frac{1}{\sqrt{N+1}}\sum_{n=0}^N \ket{N-n}_T\ket{n}_V,	
\end{align}
in the photon-number basis, where $T$ is held by the tallyman and $V$ is held by the voters.
\item Each voter $j$ applies their vote operator,
\begin{align}
	\hat{v}_j = e^{i\pi\hat{n}_V \frac{\nu_j}{N+1}},
\end{align}
where $\hat{n}_V$ is the photon-number operator for mode $V$, and $\nu_j$ is the amount cast for the $j$th voters vote.
\item Following the $m$th vote the ballot state is,
\begin{align}
	\ket{B_m} = \frac{1}{\sqrt{N+1}}\sum_{n=0}^N e^{in\Delta_m} \ket{N-n}_T\ket{n}_V,
\end{align}
where,
\begin{align}
\Delta_m = \frac{2\pi}{N+1}\sum_{j=0}^m \nu_j,
\end{align}
is a scaled sum of the votes.
\item After the $m$th vote the state observed by the tallyman is,
\begin{align}
\mathrm{tr}_V(\ket{B_m}\bra{B_m}) = \frac{1}{N+1}\sum_{n=0}^N \ket{n}_T\bra{n}_T,	
\end{align}
which contains no voting information, and similarly for the voters' reduced state.
\item After all $N$ voters have voted, the voter state $V$ is transferred to the tallyman $T$.
\item Define the tally operator as,
\begin{align}
\hat{T} = \sum_{n=0}^N n\ket{T_n}\bra{T_n},	
\end{align}
where,
\begin{align}
\ket{T_n} = \frac{1}{\sqrt{N+1}}\sum_{j=0}^N e^{inj\frac{2\pi}{N+1}}\ket{N-j}\ket{j}.	
\end{align}
\item The tallyman finds the expectation value of the tally operator,
\begin{align}
\bra{B_N}\hat{T}\ket{B_N} = \sum_{j=0}^N \nu_j,
\end{align}
yielding the sum of all the votes.
\item $\Box$
\end{enumerate}
}
\end{mdframed}
\caption{Protocol for performing secure quantum anonymous surveying.} \label{alg:quantum_voting}\index{Quantum voting}
\end{table}
